Argennon: A Scalable Cloud Based Smart Contract Platform

### 2022-07-06 tex/A.tex
Update abstract
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

\title{Argennon: A Scalable Smart Contract Platform}
\author{aybehrouz}
\date{January 2021}

\begin{document}
    \maketitle
    \begin{abstract}
        Argennon is a cloud based blockchain and smart
        contract platform which tries to solve shortcomings of existing platforms. The Argennon blockchain uses a hybrid
        proof of stake (HPoS) consensus protocol, which is based on participation of every Argennon user. This hybrid
        protocol is able to combine the benefits of a centralized and a decentralized system.

        Thanks to the cloud based design of the Argennon blockchain, transaction validation does not require costly
        computational resources, and normal personal computers with limited hardware capabilities can actively
        participate in the Argennon consensus protocol. This property makes Argennon a truly decentralized and
        democratic blockchain and one of the most secure existing platforms.

        By using cryptographic accumulators, the integrity of data on the Argennon cloud is guaranteed, and there
        is no need for trusting cloud servers. At the same time, by using a smart clustering algorithm the network usage
        and the overhead of the commitment scheme is kept manageable.

        The Argennon cloud is formed by a permission-less network of Publicly Verifiable Database (PV-DB) servers. A
        PV-DB server in Argennon, is a conventional data server which uses its computational and
        storage resources to help the Argennon network process transactions. A large portion of incentive rewards in
        the Argennon platform is devoted to PV-DB servers. This incentivizes the development of conventional
        networking, storage and computational hardware, which can benefit all areas of information technology.
    \end{abstract}
    \tableofcontents

>>>>

\title{Argennon: A Scalable Cloud Based Smart Contract Platform}
\author{aybehrouz}
\date{January 2021}

\begin{document}
    \maketitle
    \begin{abstract}
        Argennon is a next generation cloud based blockchain and smart
        contract platform. The Argennon blockchain uses
        a hybrid proof of stake (HPoS) consensus protocol, which is capable of combining the benefits of
        a centralized and a decentralized system. Thanks to the cloud
        based design of the Argennon blockchain, transaction validation does not require costly
        computational resources, and normal personal computers or smartphones, with limited hardware capabilities, can
        validate transactions and actively
        participate in the Argennon consensus protocol. This property makes Argennon a truly decentralized and
        democratic blockchain and one of the most secure existing platforms.

        The Argennon cloud is formed by a permission-less network of Publicly Verifiable Database (PV-DB) servers. A
        PV-DB server in Argennon, is a conventional data server which uses its computational and
        storage resources to help the Argennon network process transactions. A large portion of incentive rewards in
        the Argennon platform is devoted to PV-DB servers. This incentivizes the development of conventional
        networking, storage and computational hardware, which can benefit all areas of information technology.

        By using cryptographic accumulators, the integrity of data on the Argennon cloud is guaranteed, and there
        is no need for trusting cloud servers. At the same time, by using a smart clustering algorithm the network usage
        and the overhead of the cryptographic commitment scheme is kept manageable.
    \end{abstract}
    \tableofcontents

### 2022-07-06 tex/sections/avm.tex
Update abstract
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

An Argennon Standard Representation (ASR) is a programming language for describing argennon applications, optimized
for the architecture and properties of the Argennon platform.
Argennon supports two standard representations: One is a high level text based representation which needs
costly compilation before being executed on a hardware machine. The other, is a low level binary representation which
usually can be executed, with minimal pre-processing, by a JIT compiler or an emulator. The high level
language is intended for preserving the high level information of applications logic to facilitate
platform specific compiler optimization at host nodes. The low level language, on the oder hand, is designed for
efficient direct execution of applications that are not frequently used and do not benefit from compiler optimizations.

@@

The AscEE executes the requests contained in each block of the Argennon
blockchain in a three-step procedure. The first step is the \emph{preprocessing step}. In this step, the required
data for executing requests are retrieved from the Argennon cloud and the helper data structures are constructed.
This step is
designed in a way that can be done fully in parallel for each request without any risk of data races. The second
step is the \emph{Data Dependency Analysis (DDA) step}.
In this step by analyzing data dependency between requests, the AscEE determines requests that can be run in parallel
and requests that need to be run sequentially. This information is represented using an \emph{execution dag} data
structure and in the final step, requests are executed using that data structure.

@@

All Argennon prefix trees have an equal branching factor \(\beta\)\footnote{A typical choice for \(\beta\) is \(2^8\)
    .}, and
we can represent an Argennon
prefix tree as a sequence of fractional numbers\footnote{It's possible to have \(a_i=0\).
For example, \(A^{(4)}=(0.2000)_{10}\) is correct.} in base \(\beta\):
\[
    (A^{(1)},A^{(2)},A^{(3)},\dots)\ ,
\]
where \(A^{(i)}=(0.a_{1}a_{2}\dots a_{i})_\beta\), and we have \(A^{(i)} \leq A^{(i+1)}\).

>>>>

An Argennon Standard Representation (ASR) is a programming language for describing argennon applications, optimized
for the architecture and properties of the Argennon platform.
Argennon supports two standard representations: One is a high level text based representation which needs
costly compilation before being executed on a hardware machine. The other is a low level binary representation which
usually can be executed, with minimal pre-processing, by a JIT compiler or an emulator. The high level
language is intended for preserving the high level information of the application logic to facilitate
platform specific compiler optimization at a host machine. The low level language, on the oder hand, is designed for
efficient direct execution of applications that are not frequently used and do not benefit from compiler optimizations.

@@

The AscEE executes the requests contained in each block of the Argennon
blockchain in a three-step procedure. The first step is the \emph{preprocessing step}. In this step, the required
data for executing requests are retrieved from the Argennon cloud, the cryptographic proofs are verified and the
helper data structures for next steps are constructed. This step is
designed in a way that can be done fully in parallel for each request without any risk of data races. The second
step is the \emph{Data Dependency Analysis (DDA) step}.
In this step by analyzing data dependency between requests, the AscEE determines requests that can be run in parallel
and requests that need to be run sequentially. This information is represented using an \emph{execution dag} data
structure and in the final step, the requests are executed using this data structure.

@@

All Argennon prefix trees have an equal branching factor \(\beta\)\footnote{A typical choice for \(\beta\) is \(2^8\)
    .}, and
we can represent an Argennon
prefix tree as a sequence of fractional numbers in base \(\beta\):
\[
    (A^{(1)},A^{(2)},A^{(3)},\dots)\ ,
\]
where \(A^{(i)}=(0.a_{1}a_{2}\dots a_{i})_\beta\), and we have \(A^{(i)} \leq A^{(i+1)}\). \footnote{It's possible to
have \(a_i=0\). For example, \(A^{(4)}=(0.2000)_{10}\) is correct.}

### 2022-07-06 tex/sections/concurrency.tex
Update abstract
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

Every block of the Argennon blockchain contains a list of transactions. This list is an ordered list and the
effect of its contained transactions must be applied to the AVM state sequentially as they appear in the ordered
list. This ordering is solely chosen by the block proposer, and users should not have any assumptions about
the ordering of transactions in a block.

The fact that block transactions constitute a sequential list, does not mean they can not be executed and applied
to the AVM state concurrently. Many transactions are actually independent and the order of their execution does not
matter. These transactions can be safely validated in parallel by validators.

A transaction can change the AVM state by modifying either the code area or the AVM heap. In Argennon, all
transactions declare the list of memory locations they want to read or write. This will enable us to determine the
independent sets of transactions which can be executed in parallel. To do so, we define the \emph{memory dependency
graph} \(G_d\) as follows:

@@

After constructing the memory dependency graph, we can use it to construct the
\emph{execution DAG} of transactions. The execution DAG of transaction set \(T\) is a directed acyclic
graph \(G_e = (V_e,E_e)\) which has the \emph{execution invariance} property:
\begin{itemize}
    \item Every vertex in \(V_e\) corresponds to a transaction in \(T\) and vice versa.
    \item Executing the transactions of \(T\) in any order that \emph{respects} \(G_e\) will result in
    the same AVM state.
    \begin{itemize}
        \item An ordering of transactions of \(T\) respects \(G_e\) if for every directed edge \((u,v) \in E_e\)
        the transaction \(u\) comes before the transaction \(v\) in the ordering.
    \end{itemize}
\end{itemize}

Having the execution DAG of a set of transactions, using Algorithm~\ref{alg:exec_dag}, we can apply the transaction
set to the AVM state concurrently, using multiple processor, while we can be sure that the resulted AVM state will
always be the same no matter how many processor we have used.

%##\includegraphics[width=17cm]{../img/Alg1s.png}
\begin{algorithm}
    \DontPrintSemicolon
    \SetKwData{Ready}{$R_e$}\SetKwData{V}{$v_f$}\SetKwData{Graph}{$G_e$}\SetKwData{Vertices}{$V$}\SetKwData
    {Txns}{$T$}
    \KwData{The execution dag $\Graph = (\Vertices,E)$ of transaction set \Txns}
    \KwResult{The state of the AVM after applying \Txns with any ordering respecting \Graph}
    \BlankLine
    \Ready $\gets$ the set of all vertices of \Vertices with in degree 0\;
    \While{$\Vertices \neq \varnothing$}
    {
        wait until a new free processor is available\;
        \If{the execution of a transaction was finished}
        {
            remove the vertex of the finished transaction \V from \Graph\;
            \For{each vertex $u \in Adj[\V]$}
            {
                \If{$u$ has zero in degree}
                {
                    $\Ready \gets \Ready \cup u$\;
                }
            }
        }
        \If{$\Ready \neq \varnothing$}
        {
            remove a vertex from \Ready and assign it to a processor\;
        }
    }
    \caption{Executing DAG transactions}\label{alg:exec_dag}
\end{algorithm}

@@

When two transactions are dependant and they are connected with an edge \((u,v)\) in the execution DAG,
the transaction \(u\) needs to be run before the transaction \(v\). However, if \(v\) does not read any
memory locations that \(u\) modifies, we can run \(u\) and \(v\) in parallel. We just need to make sure
\(u\) does not see any changes \(v\) is making in AVM memory. This can be done by appropriate versioning
of the memory locations which is shared between \(u\) and \(v\). We call this method \emph{memory spooling}.
After enabling memory spooling between two transactions the edge connecting them can be safely removed from the
execution DAG\@.

@@

Concurrent counter data structure is a part of the AVM standard library, and any smart contract can use this data
structure for storing the balance record of highly active accounts.

>>>>

Every block of the Argennon blockchain contains a list of transactions. This list is an ordered list and the
effect of its contained transactions must be applied to the AscEE state sequentially as they appear in the ordered
list. This ordering is solely chosen by the block proposer, and users should not have any assumptions about
the ordering of transactions in a block.

The fact that block transactions constitute a sequential list, does not mean they can not be executed and applied
to the AscEE state concurrently. Many transactions are actually independent and the order of their execution does not
matter. These transactions can be safely validated in parallel by validators.

A transaction can change the AscEE state by modifying either the code area or the AscEE heap. In Argennon, all
transactions declare the list of memory locations they want to read or write. This will enable us to determine the
independent sets of transactions which can be executed in parallel. To do so, we define the \emph{memory dependency
graph} \(G_d\) as follows:

@@

After constructing the memory dependency graph, we can use it to construct the
\emph{execution DAG} of transactions. The execution DAG of transaction set \(T\) is a directed acyclic
graph \(G_e = (V_e,E_e)\) which has the \emph{execution invariance} property:
\begin{itemize}
    \item Every vertex in \(V_e\) corresponds to a transaction in \(T\) and vice versa.
    \item Executing the transactions of \(T\) in any order that \emph{respects} \(G_e\) will result in
    the same AscEE state.
    \begin{itemize}
        \item An ordering of transactions of \(T\) respects \(G_e\) if for every directed edge \((u,v) \in E_e\)
        the transaction \(u\) comes before the transaction \(v\) in the ordering.
    \end{itemize}
\end{itemize}

Having the execution DAG of a set of transactions, using Algorithm~\ref{alg:exec_dag}, we can apply the transaction
set to the AscEE state concurrently, using multiple processor, while we can be sure that the resulted AscEE state will
always be the same no matter how many processor we have used.

%##\includegraphics[width=17cm]{../img/Alg1s.png}
\begin{algorithm}
    \DontPrintSemicolon
    \SetKwData{Ready}{$R_e$}\SetKwData{V}{$v_f$}\SetKwData{Graph}{$G_e$}\SetKwData{Vertices}{$V$}\SetKwData
    {Txns}{$T$}
    \KwData{The execution dag $\Graph = (\Vertices,E)$ of transaction set \Txns}
    \KwResult{The state after applying \Txns with any ordering respecting \Graph}
    \BlankLine
    \Ready $\gets$ the set of all vertices of \Vertices with in degree 0\;
    \While{$\Vertices \neq \varnothing$}
    {
        wait until a new free processor is available\;
        \If{the execution of a transaction was finished}
        {
            remove the vertex of the finished transaction \V from \Graph\;
            \For{each vertex $u \in Adj[\V]$}
            {
                \If{$u$ has zero in degree}
                {
                    $\Ready \gets \Ready \cup u$\;
                }
            }
        }
        \If{$\Ready \neq \varnothing$}
        {
            remove a vertex from \Ready and assign it to a processor\;
        }
    }
    \caption{Executing DAG transactions}\label{alg:exec_dag}
\end{algorithm}

@@

When two transactions are dependant and they are connected with an edge \((u,v)\) in the execution DAG,
the transaction \(u\) needs to be run before the transaction \(v\). However, if \(v\) does not read any
memory locations that \(u\) modifies, we can run \(u\) and \(v\) in parallel. We just need to make sure
\(u\) does not see any changes \(v\) is making in AscEE memory. This can be done by appropriate versioning
of the memory locations which is shared between \(u\) and \(v\). We call this method \emph{memory spooling}.
After enabling memory spooling between two transactions the edge connecting them can be safely removed from the
execution DAG\@.

@@

Concurrent counter data structure is a part of the ArgC standard library, and any smart contract can use this data
structure for storing the balance record of highly active accounts.
